Supplementary Information

### 2020-11-16 doc/manuscript/MEE_manuscript.Rmd
GLS SI figures

@@

climwin_sameV_sameW_legend = "Figure S5. (PRE at SCBI)"
climwin_sameV_diffW_legend = "Figure S6. (PET at SCBI)"
climwin_diffV_diffW_legend = "Figure S7. (TMP/TMN at BCI)"
```

@@

**The relative importance of $DBH$ and climate shifted across growth metrics and climates (Figs. `r full_examples`, **S5**-**S14**).** 
The relative importance of $DBH$ tended to be least for $RW$, intermediate for $BAI$, and highest for $\Delta AGB$ (e.g., at SCBI; Fig. `r full_examples`).
However, there were exceptions, particularly when $RW$ decreased steeply with $DBH$ (e.g., at Little Tesuque; Fig. `r full_examples`).
The relative importance of climate was modest at sites including SCBI (Fig. `r full_examples`), HF (Fig. **S11**), and SC (Fig. **S14**), and stronger at sites including LT (Fig. `r full_examples`) and BCI (Fig. **S5**).

>>>>

all_GLS = "S9-S18"
GLS_BCI = "S9"
GLS_HKK = "S10"
GLS_SCBI = "S11"
GLS_LDW = "S12"
GLS_HF = "S13"
GLS_ZOF = "S14"
GLS_NE = "S15"
GLS_LT = "S16"
GLS_CB = "S17"
GLS_SC = "S18"

@@

climwin_sameV_sameW_legend = "Figure S5. (PRE at SCBI)"
climwin_sameV_diffW_legend = "Figure S6. (PET at SCBI)"
climwin_diffV_diffW_legend = "Figure S7. (TMP/TMN at BCI)"

GLS_BCI_legend = "Figure S9. Best GLS models for Barro Colorado Island (Panama)"
GLS_HKK_legend = "Figure S10. Best GLS models for Huai Kha Khaeng (Thailand)"
GLS_SCBI_legend = "Figure S11. Best GLS models for the Smithsonian Conservation Biology Institute (Virginia, USA)"
GLS_LDW_legend = "Figure S12. Best GLS models for Lilley Dickey Woods (Indiana, USA)"
GLS_HF_legend = "Figure S13. Best GLS models for Harvard Forest (Massachusetts, USA) "
GLS_ZOF_legend = "Figure S14. Best GLS models for Zofin Forest (Czech Republic)"
GLS_NE_legend = "Figure S15. Best GLS models for Niobrara/ Halsey (Nebraska, USA)"
GLS_LT_legend = "Figure S16. Best GLS models for Little Tesuque (New Mexico, USA)"
GLS_CB_legend = "Figure S17. Best GLS models for Cedar Breaks (Utah, USA)"
GLS_SC_legend = "Figure S18. Best GLS models for Scotty Creek (Northwest Territory, Canada)"
```

@@

**The relative importance of $DBH$ and climate shifted across growth metrics and climates (Figs. `r full_examples`, `r all_GLS`).** 
The relative importance of $DBH$ tended to be least for $RW$, intermediate for $BAI$, and highest for $\Delta AGB$ (e.g., at SCBI; Fig. `r full_examples`).
However, there were exceptions, particularly when $RW$ decreased steeply with $DBH$ (e.g., at Little Tesuque; Fig. `r full_examples`).
The relative importance of climate was modest at sites including SCBI (Fig. `r full_examples`), HF (Fig. `r GLS_HF`), and SC (Fig. `r GLS_SC`), and stronger at sites including LT (Fig. `r full_examples`) and BCI (Fig. `r GLS_BCI`).

### 2020-11-16 doc/manuscript/MEE_manuscript_SI.Rmd
GLS SI figures

@@

\newpage
## Figure S5. Best GLS models for Barro Colorado Island (Panama)

![**Figure S5 | Best GLS models for Barro Colorado Island (Panama) for all three growth metrics: $RW$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin* (p=previous year, c=current year). For each species, relationships are plotted if included in top model, with best-fit polynomials plotted with solid lines when both first- and second-order terms are signficant, dashed lines when only one term is signficant, and dotted lines when neither is signficant. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](tables_figures/SI_figures/composite_plots/BCI.png){ width=75% }

\newpage
## Figure S6. Best GLS models for Huai Kha Khaeng (Thailand)

![**Figure S6 | Best GLS models for Huai Kha Khaeng (Thailand) for all three growth metrics: $RW$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin* (p=previous year, c=current year). For each species, relationships are plotted if included in top model, with best-fit polynomials plotted with solid lines when both first- and second-order terms are signficant, dashed lines when only one term is signficant, and dotted lines when neither is signficant. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](tables_figures/SI_figures/composite_plots/HKK.png){ width=75% }

\newpage
## Figure S7. Best GLS models for Little Tesuque (New Mexico, USA)

![**Figure S7 | Best GLS models for Little Tesuque  (New Mexico, USA) for all three growth metrics: $RW$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin* (p=previous year, c=current year). For each species, relationships are plotted if included in top model, with best-fit polynomials plotted with solid lines when both first- and second-order terms are signficant, dashed lines when only one term is signficant, and dotted lines when neither is signficant. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](tables_figures/SI_figures/composite_plots/NewMexico.png){ width=75% }

\newpage
## Figure S8. Best GLS models for Cedar Breaks (Utah, USA)

[**Figure S8 | Best GLS models for Cedar Breaks  (Utah, USA) for all three growth metrics: $RW$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin* (p=previous year, c=current year). For each species, relationships are plotted if included in top model, with best-fit polynomials plotted with solid lines when both first- and second-order terms are signficant, dashed lines when only one term is signficant, and dotted lines when neither is signficant. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.]

\newpage
## Figure S9. Best GLS models for SCBI (Virginia, USA)

![**Figure S9 | Best GLS models for SCBI (Virginia, USA) for all three growth metrics: $RW$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin* (p=previous year, c=current year). For each species, relationships are plotted if included in top model, with best-fit polynomials plotted with solid lines when both first- and second-order terms are signficant, dashed lines when only one term is signficant, and dotted lines when neither is signficant. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](tables_figures/SI_figures/composite_plots/SCBI.png){ width=75% }

\newpage
## Figure S10. Best GLS models for Lilly Dickey Woods (Indiana, USA)

![**Figure S10 | Best GLS models for Lilly Dickey Woods (Indiana, USA) for all three growth metrics: $RW$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin* (p=previous year, c=current year). For each species, relationships are plotted if included in top model, with best-fit polynomials plotted with solid lines when both first- and second-order terms are signficant, dashed lines when only one term is signficant, and dotted lines when neither is signficant. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](tables_figures/SI_figures/composite_plots/LillyDickey.png){ width=75% }

\newpage
## Figure S11. Best GLS models for Harvard Forest (Massachusetts, USA)

![**Figure S11 | Best GLS models for Harvard Forest (Massachusetts, USA) for all three growth metrics: $RW$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin* (p=previous year, c=current year). For each species, relationships are plotted if included in top model, with best-fit polynomials plotted with solid lines when both first- and second-order terms are signficant, dashed lines when only one term is signficant, and dotted lines when neither is signficant. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](tables_figures/SI_figures/composite_plots/HarvardForest.png){ width=75% }

\newpage
## Figure S12. Best GLS models for Niobrara/ Hansley (Nebraska, USA)

\newpage
## Figure S13. Best GLS models for Zofin (Czech Republic)

![**Figure S13 | Best GLS models for Zofin (Czech Republic) for all three growth metrics: $RW$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin* (p=previous year, c=current year). For each species, relationships are plotted if included in top model, with best-fit polynomials plotted with solid lines when both first- and second-order terms are signficant, dashed lines when only one term is signficant, and dotted lines when neither is signficant. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](tables_figures/SI_figures/composite_plots/Zofin.png){ width=75% }

\newpage
## Figure S14. Best GLS models for Scotty Creek (NW Territories, Canada)

![**Figure S14 | Best GLS models for Scotty Creek (NW Territories, Canada) for all three growth metrics: $RW$, $BAI$, and $\Delta AGB$.** Precipitation and temperature group variables are as selected by *climwin* (p=previous year, c=current year). For each species, relationships are plotted if included in top model, with best-fit polynomials plotted with solid lines when both first- and second-order terms are signficant, dashed lines when only one term is signficant, and dotted lines when neither is signficant. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](tables_figures/SI_figures/composite_plots/ScottyCreek.png){ width=75% }

>>>>

GLS_BCI_legend = "Figure S9. Best GLS models for Barro Colorado Island (Panama)"
GLS_HKK_legend = "Figure S10. Best GLS models for Huai Kha Khaeng (Thailand)"
GLS_SCBI_legend = "Figure S11. Best GLS models for the Smithsonian Conservation Biology Institute (Virginia, USA)"
GLS_LDW_legend = "Figure S12. Best GLS models for Lilley Dickey Woods (Indiana, USA)"
GLS_HF_legend = "Figure S13. Best GLS models for Harvard Forest (Massachusetts, USA) "
GLS_ZOF_legend = "Figure S14. Best GLS models for Zofin Forest (Czech Republic)"
GLS_NE_legend = "Figure S15. Best GLS models for Niobrara/ Halsey (Nebraska, USA)"
GLS_LT_legend = "Figure S16. Best GLS models for Little Tesuque (New Mexico, USA)"
GLS_CB_legend = "Figure S17. Best GLS models for Cedar Breaks (Utah, USA)"
GLS_SC_legend = "Figure S18. Best GLS models for Scotty Creek (Northwest Territory, Canada)"

# ~~~~~~~~~~ (below here does not need to be copied to main doc) ~~~~~~~~~~
# Generic legends
GLS_generic_legend = " for all three growth metrics examined here. Precipitation and temperature group variables are as selected by *climwin* (p=previous year, c=current year). For each species, relationships are plotted if included in top model, with best-fit polynomials plotted with solid lines when both first- and second-order terms are signficant, dashed lines when only one term is signficant, and dotted lines when neither is signficant. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD."

@@

\newpage
## `r GLS_BCI_legend`

![`r GLS_BCI_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/BCI.png){ width=75% }

\newpage
## `r GLS_HKK_legend`

![`r GLS_HKK_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/HKK.png){ width=75% }

\newpage
## `r GLS_SCBI_legend`

![`r GLS_SCBI_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/SCBI.png){ width=75% }

\newpage
## `r GLS_LDW_legend`

![`r GLS_LDW_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/LillyDickey.png){ width=75% }

\newpage
## `r GLS_HF_legend`

![`r GLS_HF_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/HarvardForest.png){ width=75% }

\newpage
## `r GLS_ZOF_legend`

![`r GLS_ZOF_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/Zofin.png){ width=75% }

\newpage
## `r GLS_NE_legend`

``` {r eval = FALSE, echo=FALSE, warning=FALSE}

# ![`r GLS_NE_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/Nebraska.png){ width=75% }

\newpage
## `r GLS_LT_legend`

![`r GLS_LT_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/NewMexico.png){ width=75% }

\newpage
## `r GLS_CB_legend`

``` {r eval = FALSE, echo=FALSE, warning=FALSE}

# ![`r GLS_CB_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/CedarBreaks.png){ width=75% }
```

\newpage
## `r GLS_SC_legend`

![`r GLS_SC_legend` `r GLS_generic_legend`](tables_figures/SI_figures/composite_plots/ScottyCreek.png){ width=75% }
